Status and Best Practices for Reproducible Research In Plant Pathology

### 2017-08-15 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
added ability to render all formats

---
title: "Status and Best Practices for Reproducible Research In Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: 'Last update: `r Sys.Date()`'
output:
  word_document:
    keep_md: yes
    reference_docx: Phytopathology_Style_Reference.docx
csl: phytopathology.csl
bibliography: bibliography.bib
always_allow_html: yes
---

>>>>

---
title: "Status and Best Practices for Reproducible Research In Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: 'Last update: `r Sys.Date()`'
output:
  word_document:
    keep_md: yes
    reference_docx: Phytopathology_Style_Reference.docx
  pdf_document: default
  html_document: default
csl: phytopathology.csl
bibliography: bibliography.bib
always_allow_html: yes
---

<!-- 
To render all formats:
rmarkdown::render('What Does Reproducible Research Mean for Plant Pathology.Rmd', output_format = 'all')
-->
